Results

### 2019-05-03 analysis/survey/preregistration.Rmd
No indexes

TODO: The paper at <https://osf.io/u43yg> uses Bayesian hierarchical stuff and they talk a lot about index stuff. I'm not familiar with the model, though, so I don't know what applies here.

COMMENT: I don't see a need to index (i.e., use dimension reduction). We should just be collapsing covariates via Transformations in a way motivated by your experience and theory with respect to the "competing sets of covariates in the distribution of heterogeneity" that we'd like to use to compare effects on the marginal posteriors of the preference parameters.

>>>>

We will not combine any measures to create indicies.
